---
title: "beijing_ken"
output:
  html_document:
    theme: flatly
    highlight: zenburn
    number_sections: yes
    toc: yes
    toc_float: yes
    code_folding: show
---


```{r, setup, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)
```


```{r load-libraries, echo=FALSE}
library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(ggthemes)
library(GGally)
library(readxl)
library(here)
library(skimr)
library(janitor)
library(broom)
library(tidyquant)
library(infer)
library(openintro)
library(kableExtra)
```

## Exploratory Data Analysis


```{r }
beijing_data <- vroom::vroom("http://data.insideairbnb.com/china/beijing/beijing/2020-06-19/data/listings.csv.gz")%>% 
  clean_names()
## Including Plots
```

```{r}
beijing_cleaned <- beijing_data %>% 
  select(id, 
         experiences_offered, 
         host_response_time,
         host_response_rate,
         host_acceptance_rate,
         host_is_superhost,
         host_listings_count,
         host_total_listings_count,
         host_has_profile_pic,
         host_identity_verified,
         neighbourhood,
         neighbourhood_cleansed,
         zipcode,
         is_location_exact,
         property_type,
         room_type,
         accommodates,
         bathrooms,
         bedrooms,
         beds,
         bed_type,
         square_feet,
         price,
         security_deposit,
         cleaning_fee,
         guests_included,
         extra_people,
         minimum_nights,
         maximum_nights,
         number_of_reviews,
         number_of_reviews_ltm,
         review_scores_rating,
         review_scores_checkin,
         review_scores_cleanliness,
         review_scores_accuracy,
         review_scores_communication,
         review_scores_location,
         review_scores_value,
         instant_bookable,
         is_business_travel_ready,
         cancellation_policy,,
         require_guest_phone_verification,
         require_guest_profile_picture,
         reviews_per_month) %>%
  mutate(price = parse_number(price),
         cleaning_fee = parse_number(cleaning_fee),
         security_deposit = parse_number(security_deposit))
```
How many variables/columns? How many rows/observations?

There are 36283 observations each with 106 columns.
```{r}
skim(beijing_data)
```
Which variables are numbers?

41 variables are numeric.

Which are categorical or factor variables (numeric or character variables with variables that have a fixed and known set of possible values?

What are the correlations between variables? Does each scatterplot support a linear relationship between variables? Do any of the correlations appear to be conditional on the value of a categorical variable?
```{r}
selected <- beijing_data %>%
  select(price, neighbourhood_cleansed, bathrooms, bedrooms, beds,
         host_is_superhost, review_scores_rating)
         
GGally::ggpairs(selected %>% select(price, bedrooms, bathrooms), cardinality_threshold = 2000)
```

```{r}
ggplot(beijing_data, aes(x = price)) +
  geom_density()
```
