---
title: "beijing_ken"
output:
  html_document:
    theme: flatly
    highlight: zenburn
    number_sections: yes
    toc: yes
    toc_float: yes
    code_folding: show
---


```{r, setup, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)
```


```{r load-libraries, echo=FALSE}
library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(ggthemes)
library(GGally)
library(readxl)
library(here)
library(skimr)
library(janitor)
library(broom)
library(tidyquant)
library(infer)
library(openintro)
library(kableExtra)
```

## Exploratory Data Analysis


```{r }
beijing_data <- vroom::vroom("http://data.insideairbnb.com/china/beijing/beijing/2020-06-19/data/listings.csv.gz")%>% 
  clean_names()
## Including Plots
```

```{r}
skim(beijing_data)

```

```{r}

#select
beijing_selected <- beijing_data %>% 
  select(id, 
         host_response_time,
         host_response_rate,
         host_acceptance_rate,
         host_is_superhost,
         host_listings_count,
         host_total_listings_count,
         host_identity_verified,
         neighbourhood,
         neighbourhood_cleansed,
         zipcode,
         is_location_exact,
         property_type,
         room_type,
         accommodates,
         bathrooms,
         bedrooms,
         beds,
         price,
         security_deposit,
         cleaning_fee,
         guests_included,
         extra_people,
         minimum_nights,
         maximum_nights,
         number_of_reviews,
         number_of_reviews_ltm,
         review_scores_rating,
         review_scores_checkin,
         review_scores_cleanliness,
         review_scores_accuracy,
         review_scores_communication,
         review_scores_location,
         review_scores_value,
         instant_bookable,
         cancellation_policy,
         reviews_per_month) %>%
  mutate(price = parse_number(price),
         cleaning_fee = parse_number(cleaning_fee),
         security_deposit = parse_number(security_deposit),
         extra_people = parse_number(extra_people),
         host_response_rate = parse_number(host_response_rate),
         host_acceptance_rate = parse_number(host_acceptance_rate))
```
How many variables/columns? How many rows/observations?
```{r}
beijing_selected %>%
  group_by(property_type) %>%
  count(sort = TRUE)
```

There are 36283 observations each with 106 columns.

```{r}
beijing_cleaned <- beijing_selected %>%
  mutate(prop_type_simplified = case_when(
    property_type %in% c("Apartment","Condominium", "House","Loft") ~ property_type, 
    TRUE ~ "Other")) %>%
  na_if("N/A")



beijing_cleaned$cleaning_fee[is.na(beijing_cleaned$cleaning_fee)] <- 0
beijing_cleaned$security_deposit[is.na(beijing_cleaned$security_deposit)] <- 0
skim(beijing_cleaned)
```
Which variables are numbers?

41 variables are numeric.

Which are categorical or factor variables (numeric or character variables with variables that have a fixed and known set of possible values?

What are the correlations between variables? Does each scatterplot support a linear relationship between variables? Do any of the correlations appear to be conditional on the value of a categorical variable?
```{r}
#refactor things
beijing_factored <- beijing_cleaned %>%
  mutate(host_response_time = fct_relevel(host_response_time,
                                            "within an hour", 
                                            "within a few hours",
                                            "within a day",
                                            "a few days or more"),
         cancellation_policy = fct_relevel(cancellation_policy,
                                           "flexible",
                                           "moderate",
                                           "strict_14_with_grace_period"),
         prop_type_simplified = fct_relevel(prop_type_simplified,
                                          "Apartment",
                                          "Condominium",
                                          "House",
                                          "Loft",
                                          "Other"),
         room_type = fct_relevel(room_type,
                                 "Shared room",
                                 "Private room",
                                 "Entire home/apt"),
         neighbourhood_cleansed = case_when(
           neighbourhood_cleansed == "东城区" ~ "Dongcheng",
           neighbourhood_cleansed == "丰台区 / Fengtai" ~ "Fengtai",
           neighbourhood_cleansed == "大兴区 / Daxing" ~ "Daxing",
           neighbourhood_cleansed == "密云县 / Miyun" ~ "Miyun",
           neighbourhood_cleansed == "平谷区 / Pinggu" ~ "Pinggu",
           neighbourhood_cleansed == "延庆县 / Yanqing" ~ "Yanqing",
           neighbourhood_cleansed == "怀柔区 / Huairou" ~ "Huairou",
           neighbourhood_cleansed == "房山区" ~ "Fangshan",
           neighbourhood_cleansed == "昌平区" ~ "Changping",
           neighbourhood_cleansed == "朝阳区 / Chaoyang" ~ "Chaoyang",
           neighbourhood_cleansed == "海淀区" ~ "Haidian",
           neighbourhood_cleansed == "石景山区" ~ "Shijingshan",
           neighbourhood_cleansed == "西城区" ~ "Xicheng",
           neighbourhood_cleansed == "通州区 / Tongzhou" ~ "Tongzhou",
           neighbourhood_cleansed == "门头沟区 / Mentougou" ~ "Mentougou",
           neighbourhood_cleansed == "顺义区 / Shunyi" ~ "Shunyi"),
         #set neighbourhood as factor
         neighbourhood_cleansed = as.factor(neighbourhood_cleansed)) %>%
  select(-neighbourhood, -property_type)

skim(beijing_factored)
         
```
```{r}
GGally::ggpairs(beijing_factored%>% select(price, bedrooms, bathrooms), cardinality_threshold = 16)

```